Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Chad Bown, Nuno Limao, Giovanni Maggi, Anson Soderbery, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at SITE for very helpful comments and discussions.}

### 2017-01-18 draft.tex
reduce abstract to 100 words, include titlepage

\documentclass[12pt]{article}

@@

\begin{quote}
{\small Political pressure is undoubtedly an important influence in the formulation of trade agreements and the institutions that govern them. Much of the literature that speaks to the design of trade policy institutions takes the political pressure that governments face as resulting from an exogenous, stochastic process. This paper shows that when political pressure arises endogenously, important results may be overturned and new insights into the motivation for features of the trade agreements we observe and rules of organizations such as the WTO come to light. Developing a model that integrates both exogenous and endogenous political pressure and taking a general approach to the government objective function, I show that governments may want to use tariff caps both to force special interest groups to continue lobbying after a trade agreement is signed and to reduce the magnitude of that lobbying effort. The presence of endogenous politics can also destroy the ability of a traditionally-defined escape clause to provide flexibility in times of large negative political shocks when lobbies use the flexibility to seek rents. This can explain why the use of WTO Safeguards are conditioned on measurable economic indicators.}
\end{quote}

>>>>

\documentclass[12pt,titlepage]{article}

@@

\begin{quote}
{\small Much of the literature on the design of trade policy institutions takes the political pressure that governments face as exogenous. This paper integrates exogenous and endogenous political pressure into a single model, showing that the presence of endogenous political pressure overturns important results and provides insight into observed features of trade agreements as well as rules of organizations like the WTO. Endogenous politics destroys a traditionally-defined escape clause's ability to provide flexibility in the face of political shocks when lobbies use the flexibility to seek rents. This can explain why WTO Safeguard use is conditioned on measurable economic indicators.}
\end{quote}
